Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on tables

\begin{table}[h]
  \setlength{\tabcolsep}{5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
    \quickfuzz{} & 81 & 62 & 649 & 13 & 369 \\
    \midrule
    \textbf{total} & 218 &  & 972 & 34 & 852 \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & - \\
    & Timeout/OME & 23 &  \\
    & * Invalid Input & 10 & - \\    
    & * Error Message Mismatch & 3 & - \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & - \\
    & Bug & - \\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \setlength{\tabcolsep}{5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
    \quickfuzz{} & 81 & 62 & 349 & 13 & 369 \\
    \midrule
    \textbf{total} & 218 & 109 & 672 & 34 & 852 \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}
